thesis2024

### 2025-05-06 04-within-chert.qmd
Mac work session. Improved project .qmd structure for final render prep
Project organised, all articles and chapters compilled and revised

---
execute:
  echo: false
  warning: false
  message: false
  comment: "#>"
---

@@

@@

@@

For further reproducibility and replicability, and working towards the goal of open science [@Marwick2017], all analyses were performed through R Studio. The R code used for the analysis, datasets, and visual representations presented in this paper are available through our online repository (https://doi.org/10.17605/OSF.IO/DBFT2). We utilised the rrtools package by Marwick et al. [-@marwickPackagingDataAnalytical2018] to create a research compendium and produce a reproducible journal article. The repository includes the complete set of raw data used in the analysis, along with a custom R project [@wickhamPackagesOrganizeTest2015] that contains the necessary code to generate all tables and figures. To facilitate broad reuse, the code is provided under the MIT license, the data under CC‐0, and the figures under CC‐BY.

@@

## Acknowledgements

>>>>

---
execute:
  echo: false
  warning: false
  message: false
  comment: "#>"
  fig-dpi: 600
---

@@

\newpage

@@

*In preparation for publishing*

@@

For further reproducibility and replicability, and working towards the goal of open science [@marwickComputationalReproducibilityArchaeological2017], all analyses were performed through R Studio. The R code used for the analysis, datasets, and visual representations presented in this paper are available through our online repository (https://doi.org/10.17605/OSF.IO/DBFT2). We utilised the rrtools package by Marwick et al. [-@marwickPackagingDataAnalytical2018] to create a research compendium and produce a reproducible journal article. The repository includes the complete set of raw data used in the analysis, along with a custom R project [@wickhamPackagesOrganizeTest2015] that contains the necessary code to generate all tables and figures. To facilitate broad reuse, the code is provided under the MIT license, the data under CC‐0, and the figures under CC‐BY.

@@

## Acknowledgements {.unnumbered}
